\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

% McCombs Section Formatting
\titleformat{\section}{\small\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% Custom commands for consistency
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeHeading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

% Special command for projects to eliminate the "subtitle" line entirely
\newcommand{\resumeProjectHeading}[2]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\begin{document}
\pagestyle{empty}

% --- HEADING ---
\begin{center}
    {\huge \textbf{Elijah Milan D. Inamarga}} \\ \vspace{9pt}
    \small (619) 586-3265 $|$ 
    \href{mailto:elijahcek@gmail.com}{elijahcek@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/elijah-inamarga/}{linkedin.com/in/elijah-inamarga} $|$ 
    \href{https://github.com/ElijahInamarga}{github.com/ElijahInamarga}
\end{center}

% --- EDUCATION ---
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeHeading
      {San Diego State University}{\textbf{Expected May 2027}}
      {Bachelor of Science in Computer Science}{San Diego, CA}
      \begin{itemize}[leftmargin=0.2in, label=$\bullet$, nosep]
        \resumeItem{Dean's List -- \textbf{GPA: 3.8/4.0}}
        \resumeItem{Relevant Coursework: Computer Architecture, Computer Organization, Data Structures and Algorithms, Intro to Artificial Intelligence, Electricity and Magnetism, Discrete Mathematics, Linear Algebra}
      \end{itemize}
\end{itemize}

% --- EXPERIENCE ---
\section{Work Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeHeading
      {ZUM Radio Inc.}{\textbf{Jun. 2025 -- Aug. 2025}}
      {Software Engineer Intern}{Remote}
      \begin{itemize}[leftmargin=0.2in, label=$\bullet$]
        \resumeItem{Developed \textbf{DMR} and \textbf{D-STAR} audio encoding/decoding firmware for an \textbf{STM32-H723} MCU, replacing dedicated hardware.}
        \resumeItem{Profiled and debugged firmware using \textbf{GDB}, identifying performance hotspots, analyzing execution times and resource utilization.}
        \resumeItem{Optimized high-latency subroutines, cutting execution times by up to \textbf{80\%} for critical tasks, eliminating system-level bottlenecks.}
        \resumeItem{Captured \textbf{20ns}-width high-speed digital waveforms using a logic analyzer to diagnose complex \textbf{SPI} protocol timing anomalies, bit-level errors, signal integrity issues, ensuring synchronization between an \textbf{AMBE} voice codec and an \textbf{STM32-F446RE}.}
        \resumeItem{Synthesized critical protocol specifications for the \textbf{AMBE-1000} vocoder by reverse-engineering sparse documentation dating over \textbf{29} years, authoring high-fidelity technical manuals that resolved architectural ambiguities for the engineering team.}
      \end{itemize}

    \resumeHeading
      {Jersey Mike's Subs}{\textbf{Mar. 2024 -- May 2024}}
      {Crew Member}{San Diego, CA}
      \begin{itemize}[leftmargin=0.2in, label=$\bullet$]
        \resumeItem{Ensured \textbf{100\%} compliance with food safety and sanitary protocols, maintaining a sterile environment during fast-paced shifts.}
        \resumeItem{Demonstrated operational excellence in a fast-paced retail setting, managing high-volume customer orders and multi-tasking.}
        \resumeItem{Cultivated strong communication and conflict-resolution skills by engaging with a diverse customer base, efficiently processing complex transactions, and resolving service issues in a dynamic, time-sensitive environment.}
      \end{itemize}
\end{itemize}

% --- PROJECTS ---
\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeProjectHeading
      {chat-room $|$ \normalfont\small\href{https://github.com/ElijahInamarga/chat-room}{Source Code}}{\textbf{Dec. 2025 -- Present}}
      \begin{itemize}[leftmargin=0.2in, label=$\bullet$]
        \resumeItem{Developed a lightweight centralized chat server in \textbf{C} using the \textbf{Berkeley Sockets API} to facilitate real-time, bidirectional communication, enabling remote users to join a shared room and broadcast messages to all connected participants instantly.}
        \resumeItem{Implemented non-blocking IO multiplexing via the \textbf{POSIX} poll system call, enabling a single-threaded process to manage multiple network file descriptors and user inputs simultaneously without the overhead of multi-threading.}
        \resumeItem{Designed a streamlined terminal interface with manual buffer management and clear status notifications for network events, ensuring reliable data transmission within a custom \textbf{TCP/IP} architecture.}
      \end{itemize}

    \resumeProjectHeading
      {Occupi $|$ \normalfont\small\href{https://github.com/CarlosG-05/OccupyAI}{Source Code}}{\textbf{Nov. 2025}}
      \begin{itemize}[leftmargin=0.2in, label=$\bullet$]
        \resumeItem{Co-developed an end-to-end computer vision pipeline by integrating a custom-trained \textbf{YOLOv11n} model onto a \textbf{Raspberry Pi 4B} to calculate real-time headcounts and broadcasting live room occupancy metrics to a centralized visualization dashboard.}
        \resumeItem{Deployed a scalable data pipeline using a \textbf{FastAPI} backend and \textbf{Supabase} to ingest high-frequency telemetry streams.}
        \resumeItem{Integrated a dynamic \textbf{React} dashboard providing analytics for end-users to monitor real-time room occupancy levels.}
        \resumeItem{Containerized services using \textbf{Docker}, ensuring consistent deployment environments across development and implementation.}
      \end{itemize}
\end{itemize}

% --- CERTIFICATION ---
\section{Certification}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeProjectHeading
      {HAM Radio Technician License}{\textbf{Jun. 2025 -- Jun. 2035}}
      \begin{itemize}[leftmargin=0.2in, label=$\bullet$]
        \resumeItem{Certified in radio communications, technical operations, satellite communications, and various voice and digital modes.}
      \end{itemize}
\end{itemize}

% --- SKILLS ---
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:} C, C++, Python, Java, JavaScript, HTML/CSS, MIPS Assembly \\
     \textbf{Technologies \& Platforms:} Unix/Linux, POSIX, GCC/GDB,  Git, STM32, MSP430, Raspberry Pi, Arduino, Qt, React \\
     \textbf{Communication Protocols:} SPI, UART, DMR, D-STAR, TCP/IP, Berkeley Sockets \\
     \textbf{Spoken Languages:} English, Tagalog \\ 
    }}
\end{itemize}

\end{document}
